---
title: "scRNAseq Analysis"
author: "Can Ulutekin"
date: "2023-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Cleanup

```{r}
rm(list = ls())
```

### Packages

```{r}
library(tidyverse)
library(Seurat)
library(SeuratData)
library(SeuratDisk)
```

### Load Data

Please download the MS_CSF.h5ad from Schafflick et. al. before running this script.

```{r, warning=FALSE}
Convert(source = "MS_CSF.h5ad", dest = "h5seurat", overwrite = TRUE)
seuratObj <- LoadH5Seurat("MS_CSF.h5seurat")
```

### Reformat Data

Meta Data info:
- MS -> Stores binary information of MS or not
- CSF -> Stores binary information of CSF or not
- valid_clusters -> Stores binary information relating cluster validity

p.s. All binary information is stored numerically as 1 or 2, where 2 denotes TRUE and 1 denotes FALSE. So cells where MS is 2 comes from MS samples and cells where MS is 1 comes from control samples. The same holds true for the other binary variables CSF and valid_clusters.

```{r, warning=FALSE}
### Re-label 2's as TRUE and 1's as FALSE
seuratObj$MS <- seuratObj$MS == 2
seuratObj$CSF <- seuratObj$CSF == 2
seuratObj$valid_clusters <- seuratObj$valid_clusters == 2

### Remove non-valid clusters as specified by Schafflick et. al.
seuratObj <- subset(x = seuratObj, subset = valid_clusters)

### Create SeuratObject's exclusively focusing on MS, CSF or both
seuratObj_MS <- subset(x = seuratObj, subset = MS)
seuratObj_CSF <- subset(x = seuratObj, subset = CSF)
seuratObj_MS_CSF <- subset(x = seuratObj_MS, subset = CSF)

### Remove megakaryocytes and blood monocytes in CSF data due to their lack of relevance
seuratObj_CSF <- subset(x = seuratObj_CSF, labels %in% c("MegaK", "Mono") == FALSE)
seuratObj_MS_CSF <- subset(x = seuratObj_MS_CSF, labels %in% c("MegaK", "Mono") == FALSE)
```

### Figure 4.A

```{r, warning=FALSE}
cp_umap <- c("#AFD3BA", "#3F7450", "#f0ba64", "#24a5fc", "#1338be", "#890188", "#da16ff", "#f3b7ff", "#fccfca", "#f0ef70", "#80471c", "#977254", "#e70127", "#3c280d", "#3ded97")

fig4.A <- DimPlot(seuratObj_MS_CSF, reduction = "umap", group.by = "labels", pt.size = 0.5) +
  coord_fixed() +
  # scale_color_manual(values = alpha(cp_umap, 0.3)) +
  # scale_color_manual(values = alpha(cp_umap, 0.4)) +
  scale_color_manual(values = cp_umap) +
  theme_classic()

fig4.A

setwd("../figures")
pdf(file = "Figure_4A.pdf")
print(fig4.A)
invisible(dev.off())

rm(cp_umap) # cleanup
```

### Figure 4.B

```{r, warning=FALSE}
markers <- c("CD3E", "TRAC", "IL7R", "CD8B", "CCR7", "FOXP3", "TRDC", "GNLY",
             "FCGR3A", "SELL", "CD79A", "IGHD", "CD27", "CD38", "LYZ", "WDFY4",
             "FCER1A", "S100A8", "CD14", "TCF4")

fig4.B <- DotPlot(seuratObj_MS_CSF, features = markers, dot.scale = 12,
        scale = TRUE, group.by = "labels") +
  scale_color_gradientn(colours = viridis::viridis(10))

fig4.B

setwd("../figures")
pdf(file = "Figure_4B.pdf", width = 11, height = 6)
print(fig4.B)
invisible(dev.off())

rm(markers) # cleanup
```

### Figure 4.C

```{r}
fig4.C <- DotPlot(seuratObj_MS_CSF, features = c("CD70"), dot.scale = 12,
        scale = TRUE, group.by = "labels") +
  scale_color_gradientn(colours = viridis::viridis(10))

fig4.C

setwd("../figures")
pdf(file = "Figure_4C.pdf", width = 4, height = 6)
print(fig4.C)
invisible(dev.off())
```